---
title: "HW5"
author: "Shirley Liang"
date: "2022-11-13"
output: github_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

```

### Problem 1

```{r, warning=FALSE}

allnames = tibble(files = list.files("./data"))

paths = allnames %>% 
  tibble(path = list.files("./data"), ) %>% 
  mutate(
    path = str_c("data/", path),
    data = map(path, read_csv))

tidy_paths = paths %>%
  separate(files, into = c("arm", "subjectID")) %>% 
  select(arm, subjectID, data) %>% 
  unnest(data) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "result_data")

```

```{r, plot Q1}

tidy_paths %>% 
  mutate(
    arm = recode(
      arm, 
      con = "control",
      exp = "experiment" )
  ) %>% 
  ggplot(aes(x = week, y = result_data, group = subjectID, color = subjectID)) + 
  geom_line() + 
  facet_grid(.~arm) 

```


### Problem 2

```{r, raw data, warning=FALSE}

homicides = read_csv("homicide-data.csv")

```

#### In the `homicides` dataset, there are `r nrow(homicides)` observations and `r ncol(homicides)` variables, including `r names(homicides)`.

```{r, raw and summary}

homicides <- homicides %>% 
  janitor::clean_names() %>% 
  mutate(city_state = str_c(city, state, sep = ","),
  disposition_status = case_when(disposition == "Closed without arrest" ~ "unsolved",
                     disposition == "Open/No arrest" ~ "unsolved",
                     disposition == "Closed by arrest" ~ "resolved")) 

summary <- homicides %>% group_by(city_state) %>% 
  summarize(total_number_of_homicides = n(), number_of_unsolved_homicides = sum(disposition_status == "unsolved")) 

summary

```

```{r, prop.test}
# Does it make sense to prop.test one city?
Baltimore_MD_proptest <- prop.test(summary %>% filter(city_state == "Baltimore,MD") %>% pull(number_of_unsolved_homicides), 
  summary %>% filter(city_state == "Baltimore,MD") %>% pull(total_number_of_homicides)) %>% 
  broom::tidy()

# Save the output of Baltimore,MD prop.test as an R object Baltimore_MD_proptest.

# Do prop.test for all cities
all_cities <- summary %>% mutate(prop_tests = map2(.x = number_of_unsolved_homicides, .y = total_number_of_homicides, ~ prop.test(x = .x, n = .y)),
  tidy_df = map(.x = prop_tests, ~ broom::tidy(.x))) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_df) %>% 
  select(city_state, estimate, conf.low, conf.high)

all_cities

```

```{r, plot}

all_cities_plot = all_cities %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

all_cities_plot

```


### Problem 3

```{r, simulation}
set.seed(123)

sim = function(mu, n = 30, sigma = 5) {
  sim_data <- t.test(x = rnorm(n = n, mean = mu, sd = sigma), conf.int = 0.95)
  sim_data <- sim_data %>% broom::tidy(.x) %>% 
   mutate(set_mu = mu, mu_hat = estimate, p_value= p.value) %>% 
   select(set_mu, mu_hat, p_value)
}


combine_dat <- data.frame(set_mu = c(), mu_hat = c(), p_value = c())

for (j in 0:6) { 
for (i in 1:5000) {
  result_dat <- sim(j)
  combine_dat <- bind_rows(combine_dat,result_dat)
}
}

combine_dat %>% head()

```

```{r, sim plot}

power <- data.frame(set_mu = 0:6, rejected = rep(NA,7))

for(i in 1:7) {
power[i,2] <- combine_dat %>% filter(p_value < 0.05, set_mu == (i-1)) %>% count() 
power[i,2] = power[i,2]/5000
}

power_plot = power %>% ggplot(aes(x = set_mu, y = rejected)) +
  geom_point(aes(color = set_mu), size = 2) +
  geom_line(alpha = 0.3) +
  labs(x = "True value of μ",
       y = "Power of the test") +
  ggtitle("True value of μ vs. Power of the test")

power_plot

```

#### We can see form the plot that as the true value of Mu increase, power of the test increases. Therefore as the effect size increases, the power of the test increases. 

```{r, sim plot 2}

estimated_mu <- combine_dat %>% group_by(set_mu) %>% summarise(mean = mean(mu_hat))

rejected_only <- combine_dat %>% filter(p_value < 0.05) %>% group_by(set_mu) %>% summarise(mean = mean(mu_hat))

estimated_mu_plot <- estimated_mu %>% ggplot(aes(x = set_mu, y = mean)) +
  geom_point(aes(color = set_mu), size = 2) +
  geom_line(alpha = 0.3) +
  labs(x = "True value of μ",
       y = "Average estimate of μ̂")+
  ggtitle("True value of μ vs. Average estimate of μ in all simulations")


rejected_only_estimated_mu_plot <- rejected_only %>% ggplot(aes(x = set_mu, y = mean)) +
  geom_point(aes(color = set_mu), size = 2) +
  geom_line(alpha = 0.3) +
  labs(x = "True value of μ",
       y = "Average estimate of μ̂")+
  ggtitle("True value of μ vs. Average estimate of μ in samples for which the null was rejected")

```

```{r, show plot}

estimated_mu_plot

rejected_only_estimated_mu_plot

```

#### The sample average of μ̂ across tests for which the null is rejected do not approximately equal to the true value of μ when μ is below 4. This is because the power of the test increases as effect size increases, there are more proportion of times the null was rejected as μ increases. Thus, sample average of μ̂ across tests for which the null is rejected approximately equal to the true value of μ when μ is greater.
